---
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
  number_sections: true
 
title: ""
author: "[User-764Q](https://github.com/User-764Q)"
date: "`r paste0('Last Run: ', format(Sys.time(), '%A %d-%B-%Y'))`"
params: 
  param1: "Don't Forget about params"

---

<style>

#TOC {
 font-family: Calibri; 
 font-size: 16px;
 border-color: #3D68DF;
 background: #3D68DF;
}

body {
  font-family: Garamond;
  font-size: 16px; 
  border-color: #D0D0D0;
  background-color: #D0D0D0;
  color: #1A1A1A;
}

pre {
  color: #1A1A1A
  background: #D0D0D0;
  background-color: #D0D0D0
  font-family: Calibri; 
  
}

</style>

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(collapse = TRUE)

knitr::opts_chunk$set(warning = TRUE)

knitr::opts_chunk$set(message = TRUE)

knitr::opts_chunk$set(include = TRUE)

custom_black <- '1A1A1A'
custom_white <- 'C0C0C0'
custom_grey_dark <- '6F6F6F'
custom_grey_light <- 'B2B2B2'
custom_accent_blue <- '3D6BFF'

```

```{r libraries etc., message = FALSE }

library(tidyverse)

```

```{r dataload}



```

# How Hard Was S8?

Alone is one of my favourite TV shows, Ten people all by themselves try to survive 
as long as they can, last one wins a big pile of cash. No film crew or anything 
contestants film themselves and tap out when they have had enough, or get med checked
form time to time and can get pulled if they are at risk of permanent damage. 

The contestants get a choice of ten items from a list and randomly assigned an area. 

That is basically the rules. There have been 7 seasons previously. 3 in Vancouver Island, 
2 in Slave Lake one in Mongolia and one in Patagonia. 

I previously did some analysis (git), (RPub) on seasons 1- 7 and found half contestants lasted until day 40. 

Season 8 seemed particularly brutal with no contestants having much luck with fishing
which was a staple for many contestants previously. I wanted to do a quantative comparison
to see if the contestnants left earlier compared with the previous seasons on average, 
or if the reasons for leaving were different? 

## Creating Data Set

I created the data set myself from my recolection of the show and Wikipedia. 

I didn't love the categories in the Wikipedia page for why people left so I made 
my own. The hardest part was trying to judge if people were leaving because they 
didn't want to do it (for various legitimate reasons I in no way want to minimize), 
or if they were starving. I did this by deciding soley based on my own 
impression/opinion, would the contestant keep playing if they got a good meal. If
they would leave any way I put them in didn't want to do it any more, otherwise 
I put them into the medical/starvation category.

## Analysing and Aggregating Seasons 1 - 7 

## Comparing S8 To previous Seasons

### Contestants leaving first 10 days 

### Days untill half of contestants have left 

### Contestants starving/medical evacuation

## Conclusion 

I'm glad the data backed up my assumptions in general that season 8 was hard 
with more medical/starvation departures on average and half the contestants leaving 
earlier in the season. If anything this was a particularly hardy bunch because normally a few contestants drop out in the first few weeks but this time done dit. 

I hope they find somewhere else for future seasons, its great to see the contestants
sur-thrive and have at least some wins. I know it's not great watching everyone 
live all year out there but there should be a bit of a balance. When all the 
contestants are starving out, even after building a decent boat, or killing a deer
then you know its not just bad luck or lack of skills. 

```{r }

```

